Paper without a name

### 2014-05-30 Article.tex

\newcommand{\includesvg}[1]{%
  \input{#1.pdf_tex}%
}

@@

\newtheorem*{Conj*}{Conjecture}

@@

In a second step, we show how we proved this conjecture for $n$ from 2 to 6, and
how we demonstrated that the number of comparisons is an upper bound of the
optimal number of boxes for $n$ from 7 to 13 by optimizing the checking
algorithm and by constructing a precise configuration.

@@

We first define the $q$-block at position $i$ by :

$$B(q,i) = (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1)(q+2*2^i-1)$$

For example: 
$$B(0,i) = (i,i+1)$$
$$B(1,i) = (i, i+2)(i+1, i+3)$$
$$B(2, i) = (i,i+4)(i+1,i+5)(i+2,i+6)(i+3,i+7)$$

Then, for $n=2^p$ we define for $q < p$ the $(p,q)$-line by :

$$L(p,q) = B(q,0) B(q,2^{q+1}) \cdots B(q,2^p-2^{q+1})$$

@@

$$C_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$$

@@

>>>>

\newcommand{\includesvg}[1]{%
  \input{#1.pdf_tex}%
}
\newcommand{\comp}{\operatornamewithlimits{\bigcirc}}

@@

\newtheorem*{Conj*}{Conjecture}
\newtheorem*{def*}{Définition}

@@

In a second step, we show how we experimentally checked this conjecture for $n$ from 2 to 6, and
how we demonstrated that the number of comparisons is an upper bound of the
optimal number of boxes for $n$ from 7 to 13 by optimizing the checking
algorithm and by constructing a precise configuration.

@@

We first define $B(q,i)$, the $q$-block at position $i$ by :

\begin{def*}
$B(q,i) = (q,q+2^i)(q+1,q+1+2^i)\cdots(q+2^i-1,q+2*2^i-1) = \overset{2^{i}-1}{\underset{j=0}{\bigcirc}} (q+j,q+j+2^i)$
\end{def*}
For example: 
$$B(q,0) = (q,q+1)$$
$$B(q,1) = (q, q+2)(q+1, q+3)$$
$$B(q,2) = (q,q+4)(q+1,q+5)(q+2,q+6)(q+3,q+7)$$

Then, for $n=2^p$ we define $L(p,q)$, for $q < p$ the $(p,q)$-line by :

\begin{def*}
$L(p,q) = B(q,0) B(q,2^{q+1}) \cdots B(q,2^p-2^{q+1})$
\end{def*}

@@

\begin{def*}
$C_{2^p}^0 = L(p,0) L(p,1) L(p,2) \cdots L(p,p-1) L(p,p-2) \cdots L(p,1) L(p,0)$
\end{def*}

@@

\begin{Conj*}
$C_n^0$ generates all permutations fon $n$
\end{Conj*}
